Methods for Large Scale Learning to Rank

### 2014-11-13 report/Chapters/Background.tex
dolf :)

%************************************************
This chapter is written with the goal to provide the reader with a brief introduction in the Learning to Rank field and the MapReduce computational model. Models and theories explained in this chapter can be regarded as prior knowledge needed to understand the subsequent chapters of this thesis.
\section{A basic introduction to Learning to Rank}
Different definitions of Learning to Rank exist. In general, all ranking methods that use machine learning technologies to solve the problem of ranking are called Learning to Rank methods. Figure \ref{fig:discriminative_training} describes the general process of machine learning. Input space $X$ consists of input objects $x$. A hypothesis $h$ defines a mapping of input objects from $X$ into the output space $Y$, resulting in prediction $\hat{y}$. The loss of an hypothesis is the difference between the predictions made by the hypothesis and the correct values mapped from the input space into the output space, called the \emph{ground truth labels}. The task of machine learning is to find the best fitting hypothesis $h$ from the set of all possible hypotheses $H$, called the hypothesis space.\\

>>>>

This chapter provides an introduction to Learning to Rank and MapReduce. Knowledge about the models and theories explained in this chapter is required to understand the subsequent chapters of this thesis.
\section{A basic introduction to Learning to Rank}
Different definitions of Learning to Rank exist. In general, all ranking methods that use machine learning technologies to solve the problem of ranking are called Learning to Rank methods. Figure \ref{fig:discriminative_training} describes the general process of machine learning. Input space $X$ consists of input objects $x$. A hypothesis $h$ defines a mapping of input objects from $X$ into the output space $Y$, resulting in prediction $\hat{y}$. The loss of an hypothesis is the difference between the predictions made by the hypothesis and the correct values mapped from the input space into the output space, called the \emph{ground truth labels}. The task of machine learning is to find the best fitting hypothesis $h$ from the set of all possible hypotheses $H$, called the hypothesis space.\\
